---
title: "MATH 121: Calculus and Analytic Geometry I"
format: 
  html:                     
    toc: true
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## Course Description

This is the first course for Actuarial Mathematics, Applied Math and Statistics, Applied Economics, Biology and Environmental Science majors, and those concentrating in Applied Statistics. The course is also recommended for the math minors. Topics include limits, continuity, derivatives, and integrals, along with their application to the Mean Value Theorem, curve sketching and optimization, the calculus of transcendental functions, and area between curves.

## Office Hours 

Tuesday and Thursday: 12:30pm - 2:00pm, Friday: 12-1pm (on Zoom), or by appointment 

[Office hour Zoom Link](https://bryant.zoom.us/j/4419675207)

## Textbook

Calculus, 10th Edition by Howard Anton, Irl C. Bivens, Stephen Davis, Wiley& Sons, Inc. ©2012, ISBN: 978-0-470-64772-1

## Course Objectives

The primary goals of this course are to provide the student with the capabilities to understand problems in differential and integral calculus and apply the appropriate methods to solve them. After taking this course, the student should be able to

-   explain the concept of limits, average rate of changes,derivatives and differentiation

-   calculate basic limits, derivatives and differentiation using appropriate rules

-   graph functions using first and second derivatives

-   formulate and solve certain types of optimization problems

-   explain and calculate definite integrals of a variety of functions

## Grades

```{r}
# install.packages("ggplot2")
library(ggplot2)
library(dplyr)
# Variables

Percentage = c(.6, .3, .07, .03)
Grades = c('Midterm Exams', 'Final Exam', 'Homework','Attendance')
label2 = paste0(Grades, " ", Percentage*100, "%")

df = data.frame(Grades = Grades, Percentage = Percentage, labels = label2)

ggplot(df, aes(x = "", y = Percentage, fill = Grades)) +
  geom_col() +
  geom_label(aes(label = labels),
             position = position_stack(vjust = 0.5),
             show.legend = FALSE) +
  labs(x='')+
  coord_polar(theta = "y")+
  theme_void()
```

-   *Final Exam*: The final exam is comprehensive covering all the topics of the course.  The problems in the exam will be similar to those in the homework assignments. A formula sheet (1 page) is allowed. Calculators with only basic calculations are allowed.

-   *Midterm Exams*: Tentatively, there are three Midterm exams, and each is worth 20%. A formula sheet (1 page) is allowed. Makeup exam will only be given to students who provide a valid written excuse BEFORE the date of the exam. The approved makeup exam should be taken no later than a week after the actual one. The grades posted on Canvas are official, and permanent after a week they are posted. The problems in the exams will be similar to those in the homework assignments.

-   *Homework*: The homework assignment will be collected weekly through Canvas. You can type or hand-write and scan the homework then upload them to Canvas for grading. Completing all the problems of the homework will guarantee you at least 50% of the grades.

-   *Attendance*: Attendance will be checked regularly in class. The grade for attendance (3%) is usually enough to move up a letter grade. You are responsible for obtaining course material missed during an absence.


## Grades Scale

The numerical grades are converted to letter grades as follows.

|     |                |     |                |
|-----|----------------|-----|----------------|
| A   | 92.45 - 100%   | C   | 72.45 - 76.44% |
| A-  | 89.45 - 92.44% | C-  | 69.45 - 72.44% |
| B+  | 86.45 - 89.44% | D+  | 66.45 - 69.44% |
| B   | 82.45 - 86.44% | D   | 59.45 - 66.44% |
| B-  | 79.45 - 82.44% | F   | Below 59.44%   |
| C+  | 76.45 - 79.44% |     |                |

```{r}
library(ggplot2)
library(forcats)

# Basic barplot

Grades           = c("A","A-","B+","B","B-","C+","C","C-","D+","D", "F")
Total_Percentage = c(92.45, 89.45, 86.45, 82.45 ,79.45, 76.45, 72.45, 69.45, 66.45, 59.45, 0)
df = data.frame(Grades = Grades, Total_Percentage = Total_Percentage)


p<-ggplot(data=df, aes(x= fct_rev(fct_reorder(Grades, Total_Percentage)), y=Total_Percentage)) +
  geom_col(fill="steelblue")+
  labs(y = 'Total Percentage', x ='Letter Grade')+
  geom_text(aes(label = Total_Percentage), vjust = -0.5)+
  theme_minimal()
p

```

## Tentative Topics

- Chapter 1: Limits and continuity
- Chapter 2: The derivative
- Chapter 3: The derivative in graphing and application
- Chapter 4: Integration
- Chapter 5: Application of the definite Integral 

## Sustainable Development Goals

We will occasionally discuss and work with data related to the United Nation Sustainable Development Goals. These goals are called by the UN for action in a global partnership to provide peace and prosperity for people and the planet, now and into the future. Specifically, we will focus one of the following six SDGs:

  - [SDG 3](https://www.globalgoals.org/goals/3-good-health-and-well-being/): Good Health & wellbeing	
  - [SDG 4](https://www.globalgoals.org/goals/4-quality-education/): Quality Education	
  - [SDG 8](https://www.globalgoals.org/goals/8-decent-work-and-economic-growth/): Decent Work and Economic Growth
  - [SDG 7](https://www.globalgoals.org/goals/7-affordable-and-clean-energy/): Affordable and Clean Energy	
  - [SDG 9](https://www.globalgoals.org/goals/9-industry-innovation-and-infrastructure/): Industry, Innovation, and Infrastructure	
  - [SDG 11](https://www.globalgoals.org/goals/11-sustainable-cities-and-communities/): Sustainable Cities and Communities



You can learn more about the Sustainable Development Goals at: https://sdgs.un.org/goals

[Sustainable Development Goals](https://sdgs.un.org/goals)


## Academic Misconduct

Cheating will result in an F as your final grade and may result in your expulsion from the University. All cheating will be reported to the Chair of the Mathematics Department and Academic Advising.

## Regarding Diversity

In this course, and all your courses at Bryant, and throughout the Bryant learning community, we value and respect diversity. This includes differences in race, ethnicity, nationality, gender, gender identity, sexuality, socioeconomic status, ability, and religion.


